Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-09-03 Manuscript/00-main.Rmd
Run pipeline
Update Real Data Analysis
Update draft

---
title: Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data
author:
- name: Boyi Guo*
  num: a
- name: Byron C. Jaeger
  num: b 
- name: AKM Fazlur Rahman
  num: a   
- name: D. Leann Long
  num: a  
- name: Nengjun Yi
  num: a
address:
- num: a
  org: Department of Biostatistics, University of Alabama at Birmingham, Birmingham, USA
- num: b
  org: Department of Biostatistics and Data Science, Wake Forest University, Winston-Salem, USA
corres: "*Corresponding author name, This is sample corresponding address. \\email{xxx@uab}"
presentaddress: This is sample for present address text this is sample for present address text
authormark: Guo et al.
articletype: Research article
received: 2021-01-01
revised: 2021-02-01
accepted: 2021-03-01
abstract: "Spike-and-slab priors have been extensively studied for variable selection, and recently been extended to function selection in generalized additive models (GAMs). Most of the previous works on fitting spike-and-slab GAM relies on Markov chain Monte Carlo (MCMC) algorithms to identify the promising subsets of functions. The computational burden of MCMC makes these models less feasible, especially in high-dimensional setting. Besides, most of the current spike-and-slab GAM consider an “all-in-all-out” approach for function selection, rendering less flexibility to answer if non-linear effects are necessary in the model. We propose Bayesian hierarchical generalized additive models for function selection and prediction. The proposed models employ spike-and-slab priors, mixture normal and mixture double exponential, for smooth and sparse solution. Two EM based algorithms, EM-IWLS and EM-Coordinate Descent, are developed for accelerated computation. Simulation studies and real data analysis demonstrated improved performance against the state-of-art models, mgcv and COSSO. The software implementation of the proposed methods is freely available via the R package BHAM."
keywords: Spike-and-Slab Priors; High-Dimensional Data; Generalized Additive Models; EM-IWLS; EM-Coordinate Decent
bibliography: bibfile.bib
output: 
  rticles::sim_article:
    keep_tex: TRUE
header-includes: 
  - \usepackage{tikz}
  - \usepackage{pgfplots}
---

@@

tar_load(tab_binom)
tar_load(tab_gaus)
```

>>>>

---
title: Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data
author:
- name: Boyi Guo*
  num: a
- name: Byron C. Jaeger
  num: b 
- name: AKM Fazlur Rahman
  num: a   
- name: D. Leann Long
  num: a  
- name: Nengjun Yi
  num: a
address:
- num: a
  org: Department of Biostatistics, University of Alabama at Birmingham, Birmingham, USA
- num: b
  org: Department of Biostatistics and Data Science, Wake Forest University, Winston-Salem, USA
corres: "Nengjun Yi, epartment of Biostatistics, University of Alabama at Birmingham, Birmingham, USA. \\email{nyi@uab.edu}"
presentaddress: This is sample for present address text this is sample for present address text
authormark: Guo et al.
articletype: Research article
received: 2021-01-01
revised: 2021-02-01
accepted: 2021-03-01
abstract: "Spike-and-slab priors have been extensively studied for variable selection, and recently been extended to function selection in generalized additive models (GAMs). Most of the previous works on fitting spike-and-slab GAM relies on Markov chain Monte Carlo (MCMC) algorithms to identify the promising subsets of functions. The computational burden of MCMC makes these models less feasible, especially in high-dimensional setting. Besides, most of the current spike-and-slab GAM consider an “all-in-all-out” approach for function selection, rendering less flexibility to answer if non-linear effects are necessary in the model. We propose Bayesian hierarchical generalized additive models for function selection and prediction. The proposed models employ spike-and-slab priors, mixture normal and mixture double exponential, for smooth and sparse solution. Two EM based algorithms, EM-IWLS and EM-Coordinate Descent, are developed for accelerated computation. Simulation studies and real data analysis demonstrated improved performance against the state-of-art models, mgcv and COSSO. The software implementation of the proposed methods is freely available via the R package BHAM."
keywords: Spike-and-Slab Priors; High-Dimensional Data; Generalized Additive Models; EM-IWLS; EM-Coordinate Decent
bibliography: bibfile.bib
output: 
  rticles::sim_article:
    keep_tex: TRUE
header-includes: 
  - \usepackage{tikz}
  - \usepackage{pgfplots}
---

@@

tar_load(tab_binom)
tar_load(tab_gaus)

tar_load(ful_dat)
tar_load(tbl_one)
tar_load(bamlasso_tune)
tar_load(bai_cv_res)
```
